Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-08 paper.qmd
Update Fig10

distance_points <- ggplot(
  distance_two_curvy_dist, 
  aes(x = as.numeric(bin),
      y = dist_highd)) +
  geom_point(alpha = 0.5) +
  geom_jitter() +
  scale_x_continuous(breaks = sort(unique(as.numeric(distance_two_curvy_dist$bin))),
                     labels = c(
                       expression(a[1]),
                       expression(2*a[1]),
                       expression(3*a[1]),
                       expression(4*a[1]),
                       expression(5*a[1]),
                       expression(6*a[1]),
                       expression(7*a[1]),
                       expression(8*a[1])
                     )) +
  # geom_vline(xintercept = 2,
  #            linetype="solid",
  #            color = "#bdbdbd",
  #            linewidth=1) +
  # geom_vline(xintercept = 4.5,
  #            linetype="solid",
  #            color = "#bdbdbd",
  #            linewidth=1) +
  ylab(expression(d^{(7)})) +
  xlab(expression(d^{(2)})) +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

```{r}
#| label: fig-rm-lg
#| fig-cap: "Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal: (b) benchmark = 4.5$a_1$ and (c) benchmark = 2$a_1$, where $a_1$ = 0.09."
#| fig-height: 15
#| fig-width: 15
#| out-height: 70%

wrap_plots(distance_points,distance_hist, ncol = 2) / wrap_plots(trimesh_two_curvy2, trimesh_two_curvy_removed2, trimesh_two_curvy_removed1,
two_curvy_proj_umap_model_delaunay,
two_curvy_proj_umap_model_benchmark2,
two_curvy_proj_umap_model, ncol = 3) 
```

>>>>

distance_points <- ggplot(
  distance_two_curvy_dist, 
  aes(x = as.numeric(bin),
      y = dist_highd)) +
  geom_point(alpha = 0.5) +
  #geom_jitter() +
  scale_x_continuous(breaks = sort(unique(as.numeric(distance_two_curvy_dist$bin))),
                     labels = c(
                       expression(a[1]),
                       expression(2*a[1]),
                       expression(3*a[1]),
                       expression(4*a[1]),
                       expression(5*a[1]),
                       expression(6*a[1]),
                       expression(7*a[1]),
                       expression(8*a[1])
                     )) +
  # geom_vline(xintercept = 2,
  #            linetype="solid",
  #            color = "#bdbdbd",
  #            linewidth=1) +
  # geom_vline(xintercept = 4.5,
  #            linetype="solid",
  #            color = "#bdbdbd",
  #            linewidth=1) +
  ylab(expression(d^{(7)})) +
  xlab(expression(d^{(2)})) +
  #ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

```{r}
#| label: fig-rm-lg
#| fig-cap: "Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal: (b) benchmark = 4.5$a_1$ and (c) benchmark = 2$a_1$, where $a_1$ = 0.09."
#| fig-height: 4
#| fig-width: 20

free(distance_points) + plot_annotation(tag_levels = 'A') +
 (trimesh_two_curvy2 + trimesh_two_curvy_removed2 + trimesh_two_curvy_removed1 + two_curvy_proj_umap_model_delaunay + two_curvy_proj_umap_model_benchmark2 + two_curvy_proj_umap_model) +
  plot_layout(widths = c(0.5, 1, 1, 1)) +
  plot_annotation(tag_levels = list(c("(a)", "(b)"))) 
```
